From Freebase to Wikidata: The Great Migration

### 2015-10-16 paper.tex
Subdivided related work section (still needs content)

@@

\begin{figure*}[!ht]
    \centering
    \begin{subfigure}[b]{1.0\columnwidth}
        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
        \caption{Spatio-temporal distribution of Freebase.}
        \label{fig:freebase}
    \end{subfigure}
    \begin{subfigure}[b]{1.0\columnwidth}
        \includegraphics[width=\textwidth]{img/wikidata-projection-bw.pdf}
        \caption{Spatio-temporal distribution of Wikidata.}
        \label{fig:wikidata}
    \end{subfigure}
    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
      from the year 0 to 2015, following a~power law ($y' = y^8$).}
    \label{fig:time-space}
\end{figure*}

@@

There has been a lot of research on ontology mapping.

>>>>

\begin{figure*}[h]
    \centering
    \begin{subfigure}[b]{1.0\columnwidth}
        \includegraphics[width=\textwidth]{img/freebase-projection-bw.pdf}
        \caption{Spatio-temporal distribution of Freebase.}
        \label{fig:freebase}
    \end{subfigure}
    \begin{subfigure}[b]{1.0\columnwidth}
        \includegraphics[width=\textwidth]{img/wikidata-projection-bw.pdf}
        \caption{Spatio-temporal distribution of Wikidata.}
        \label{fig:wikidata}
    \end{subfigure}
    \caption{Spatio-temporal distribution of Freebase and Wikidata items,
      the $x$ axis shows longitude degrees from 180°~E to 180°~W, the $y$ axis shows time
      from the year 0 to 2015, following a~power law ($y' = y^8$).}
    \label{fig:time-space}
\end{figure*}

@@

@@

For the challenges listed in \autoref{section:challenges-of-the-migration}
there is a body of work dealing with it. In many cases, the problems we have encountered in
this migration have turned out to be much simpler than the problems solved in existing research.

\textbf{Data licensing.}
Only dealing with two open licenses.

\textbf{Topic mappings.}
Since both databases build on Wikipedia...

\textbf{Schema mappings.}
There has been extensive research on the topic of mapping the structures
of two databases or knowledge bases~\cite{mappingsurvey1,mappingsurvey2,mappingsurvey3}.
The current work is, in many technical respects, rather simple:
we are looking for a one-directional mapping (since the case of data
flowing from Wikidata back to Freebase is not relevant),
for a one-off data flow (since Freebase is now read-only),
evaluated by human contributors (therefore the quality of the mapping

\textbf{Data maintenance.}
Should also cover references (kvault) and quality.
